Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-09-27 schedule.tex
just begin
init on mac

\subsection{Service Construct} % (fold)
\label{sub:service_construct}

% subsection service_construct (end)

\subsection{Matching} % (fold)
\label{sub:matching}

% subsection matching (end)

\subsection{Oredr Flow} % (fold)
\label{sub:oredr_flow}

% subsection oredr_flow (end)

\subsection{Rating and Recommand System} % (fold)
\label{sub:rating_&_recommand_system}

% subsection rating_&_recommand_system (end)

@@

\subsection{Scheduling} % (fold)
\label{sub:scheduling}

% subsection scheduling (end)
% section model (end)

>>>>

In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the resources scheduling process in Cloud Manufacturing Ecosystem.

Most of the related methodologies can be archived into \textbf{four} main modules, namely \textit{Decision Making Support}, \textit{Rating Schema}, \textit{Recommand System} and \textit{Matching Regulation}, which are going to explained in detail respectively.

The scheduling effect can be estimated and observed through \textit{Service Dashboard}, which also provides the control function that will help the evolution in the Ecosystem.

@@

\subsection{Rating Schema} % (fold)
\label{sub:rating_schema}

% subsection rating_schema (end)

\subsection{Recommand System} % (fold)
\label{sub:recommand_system}

% subsection recommand_system (end)

\subsection{Matching Regulation} % (fold)
\label{sub:matching_regulation}

% subsection matching_regulation (end)

\subsection{Service Dashboard} % (fold)
\label{sub:service_dashboard}

% subsection service_dashboard (end)
% section model (end)
